\documentclass[11pt,a4paper]{letter}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}

\begin{document}

\begin{letter}

\opening{Dear Hiring Manager,}

\vspace{2mm}

I am writing to express my interest in Data \& AI Engineer / Generative AI roles within your organization. With over three years of experience in building enterprise AI systems and data platforms, I specialize in LLM engineering, Retrieval-Augmented Generation (RAG), and financial data intelligence solutions.

Currently, I am working as a Consultant (via Mindsprint, Olam Group) on a Bain \& Company-led engagement for Biocon, where I design and deploy large-scale AI solutions for financial spend intelligence. I developed an LLM-powered spend classification system leveraging RAG pipelines, vector databases, and semantic search to map complex SAP financial transactions into structured taxonomies. This significantly improved data accuracy, reduced manual effort, and enhanced decision-making across procurement and finance functions.

In addition, I have built scalable data architectures using Azure Databricks and Azure Data Factory, engineering end-to-end ETL/ELT pipelines to process high-volume financial data into a governed lakehouse. This enabled audit-ready reporting and advanced analytics such as SpendCube, supporting multi-year financial insights and enterprise data governance.

My expertise includes working with LLM ecosystems such as LangChain and LlamaIndex, along with multi-agent frameworks, where I focus on optimizing retrieval quality, improving model performance, and deploying reliable AI systems in production environments using FastAPI and cloud infrastructure.

I am particularly interested in opportunities where I can further advance AI-driven financial analytics, build robust RAG systems, and contribute to impactful Generative AI applications at scale. I am confident that my experience working on consulting-driven enterprise AI engagements will allow me to deliver meaningful value to your team.

\closing{Sincerely,}

\vspace{2mm}
Ashley Nand

\end{letter}

\end{document}