
\textcolor[RGB]{0,128,128}{\textbf{Kofi: Study Assistant using CrewAI, RAG, Docker, EC2}} \hfill \textit{Oct 2025 – Nov 2025} \\
\textbf{Technologies:} Python, CrewAI, LlamaIndex, ChromaDB, Streamlit, FastAPI, Groq, Docker, AWS EC2 \\
Engineered a RAG-based PDF question-answering system leveraging LlamaIndex and ChromaDB for highly efficient vector search. Developed a robust FastAPI + CrewAI backend and an intuitive Streamlit frontend, containerized with Docker and deployed seamlessly on AWS EC2. Optimized embeddings and prompt strategies to deliver precise, context-aware, and reliable responses.

\vspace{1em}

\textcolor[RGB]{0,128,128}{\textbf{The Bible Stories}} \hfill \textit{Nov 2024 – Dec 2024} \\
\textbf{Technologies:} MySQL, React, Express, Node.js, Tailwind CSS, Ubuntu, GitHub \\
Built a secure, scalable full-stack web application for content management and publication of Bible-related resources. Implemented user authentication, optimized backend APIs, and orchestrated CI/CD pipelines for high-performance deployment.

\vspace{1em}

\textcolor[RGB]{0,128,128}{\textbf{Time Series Data Analysis – The University of Auckland, New Zealand}} \hfill \textit{Nov 2021 – May 2023} \\
\textbf{Technologies:} Machine Learning, Python, Big Data \\
Conducted advanced time-series modeling, forecasting, and evaluation on real-world datasets. Generated actionable insights for time-dependent data under the mentorship of Dr. Andreas W. Kempa-Liehr.

\vspace{1em}

\textcolor[RGB]{0,128,128}{\textbf{Psychological Emotion-Based Classification of EEG Variations (Data Analytics)}} \hfill \textit{Oct 2021 – Nov 2022} \\
\textbf{Technologies:} Neuroscience, EEG Signals, MATLAB, Big Data \\
Designed algorithms to classify emotional states from EEG signals by identifying optimal threshold patterns. Extracted and analyzed patterns for accurate emotion recognition across valence, arousal, and dominance dimensions.

\vspace{1em}

\textcolor[RGB]{0,128,128}{\textbf{Product Vending Machine with Machine Learning (IoT Project)}} \hfill \textit{Mar 2022 – May 2022} \\
\textbf{Technologies:} Arduino, Sensor Technology, IoT, Machine Learning \\
Developed a smart vending machine integrated with IoT sensors and RFID-based authentication. Applied machine learning to analyze seasonal sales trends and generate recommendations for top-selling products.

\vspace{1em}

\textcolor[RGB]{0,128,128}{\textbf{Medicare for e-Health Data Management Technologies (Android App)}} \hfill \textit{Feb 2021 – Jun 2021} \\
\textbf{Technologies:} Android Development, Room DB, Firebase, MVVM \\
Developed an Android application for patient treatment record management with offline-first storage (Room DB) \& real-time cloud sync (Firebase). Ensured maintainable, scalable architecture using MVVM, improving reliability and user accessibility.